Errata

### 2025-04-17 tex/Manuscript-4.tex
Update dissertation files: add new taxa, improve formatting, and enhance data availability statements

Sequencing was performed at Eurofins Genomics (Konstanz, Germany) on an Illumina MiSeq generating \(2\times 300\)\,bp paired-end reads. The sequencing library was demultiplexed using \texttt{cutadapt} v3.4 \citep{Martin2011} using the following parameters: \texttt{-e 0.2 -q 15,15 -m 150 --discard-untrimmed}. The ASVs were generated using trimmed reads and the \texttt{DADA2} package v1.20 \citep{Callahan2016} with R v4.1 using the pooled approach with the following parameters: \texttt{truncLen=c(240,200), maxN=0, rm.phix=TRUE, minLen=200}. Taxonomic assignment was done using \texttt{DADA2} and the SILVA database v138 \citep{Quast2012}. 
Subsequently, ASVs representing chloroplasts, mitochondria and singletons were removed.

>>>>

Sequencing was performed at Eurofins Genomics (Konstanz, Germany) on an Illumina MiSeq generating \(2\times 300\)\,bp paired-end reads. The sequencing library was demultiplexed using \texttt{cutadapt} v3.4 \citep{Martin2011} using the following parameters: \texttt{-e 0.2 -q 15,15 -m 150 --discard-untrimmed}. The ASVs were generated using trimmed reads and the \texttt{DADA2} package v1.20 \citep{Callahan2016} with R v4.1 using the pooled approach with the following parameters: \texttt{truncLen = c(240,200), maxN = 0, rm.phix = TRUE, minLen = 200}. Taxonomic assignment was done using \texttt{DADA2} and the SILVA database v138 \citep{Quast2012}. 
Subsequently, ASVs representing chloroplasts, mitochondria and singletons were removed.
